Location of Salmon Farms

### 2021-03-23 marine_mapping_archive_v1/marine_fish_general/food_pressures/finfish_nutrient/step1_nutrient.Rmd
Finished reorganizing data

## Read in fao data and get a species list for salmon
species_list <- read.csv(here("aquaculture/marine/STEP1_species_groups/int/marine_groups.csv"))  %>%
  distinct(species, aq_group)

>>>>

## Read in fao data and get a species list for salmon
species_list <- read.csv(here("marine/STEP1_species_groups/int/marine_groups.csv"))  %>%
  distinct(species, aq_group)

### 2021-03-23 marine_mapping_archive_v1/salmon/food_pressures/salmon_disturbance/STEP2_occupancy_distribution.Rmd
Finished reorganizing data

##Conversion Table
Read in and save the necessary values from the salmon conversion table
```{r parameters from conversion table}
salmon_conversion <- read_csv(here("aquaculture/marine/salmon/salmon_disturbance/data/salmon_conversion_factors.csv"))

>>>>

##Conversion Table
Read in and save the necessary values from the salmon conversion table
```{r parameters from conversion table}
salmon_conversion <- read_csv(here("marine/salmon/food_pressures/salmon_disturbance/data/salmon_conversion_factors.csv"))

### 2021-03-23 marine_mapping_archive_v1/salmon/food_pressures/salmon_ghg/STEP1_ghg_emissions.Rmd
Finished reorganizing data

fao <- read.csv(here("aquaculture/data/fao_mariculture_clean.csv")) %>%
  filter(environment %in% c("Marine", "Brackishwater"))

## Read in fao data and get a species list for salmon 
species_list <- read.csv(here("aquaculture/marine/species_groups/int/marine_groups.csv"))  %>%
  distinct(species, aq_group)

>>>>

fao <- read.csv(here("data/fao_aquaculture_clean.csv")) %>%
  filter(environment %in% c("Marine", "Brackishwater"))

## Read in fao data and get a species list for salmon 
species_list <- read.csv(here("marine/species_groups/int/marine_groups.csv"))  %>%
  distinct(species, aq_group)

### 2021-03-23 marine_mapping_archive_v1/salmon/salmon_farm/STEP2_salmon_farm_locations.Rmd
Finished reorganizing data

Now we will map the remaining countries with shrimp farms. Workflow will be as follows: 
 - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
 - If there are not exact locations or comprehensive locations, find the number of farms. 
 - If there is no information at all, note it.

For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1). 
 5: Comprehensive number of exact farms

4: Subset of exact locations, need to add a specific number of farms to existing locations. 
  - country|species|farm locations
  - country|species|additional points

3: A specific number of farms are known, but no locations 
 - country|species|additional points

2: Exact locations are a subset of total farms. But the number of total farms are unknown. Need to be gapfilled by tonnage.

1: No information on number of farms at all. Need to be gapfilled by tonnage. 
 - country|species|# additional farms (this will be NA)

@@

# save as a dataframe
farms_chile <- data.frame(do.call(rbind, st_geometry(chile_pts))) 
names(farms_chile) <- c("lon", "lat")
farms_chile <- farms_chile %>%
  mutate(iso3c="CHL") %>%
  mutate(data_quality = 5)

write_csv(farms_chile, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_chile.csv"))

@@

We use the number of salmon licenses to get a proxy for the relative distribution of production along the Norwegian coast. 
†
## Load csv with lat long
Comprehensive License data.

@@

farms_nor <- sub_norway %>% 
  distinct(lon=Ø_GEOWGS84, lat=N_GEOWGS84, iso3c="NOR") %>% # Counting duplicate liscense locations once
  mutate(data_quality = 5)

write_csv(farms_nor, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_nor.csv"))

norway <- read_csv(here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_nor.csv"))

@@

# Scotland
 - Comprehensive data

@@

farms_scotland$subregion <- sub_scotland$subregion
farms_scotland <- farms_scotland %>%
  mutate(iso3c = "GBR") %>%
  mutate(data_quality = 5)

write_csv(farms_scotland, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_scotland.csv"))

@@

 - Even though it is ASC, all indications point to that it is comprehensive.

@@

farms_fro <- data.frame(do.call(rbind, st_geometry(fro_pts_latlon))) 
names(farms_fro) <- c("lon", "lat")
farms_all_fro <- farms_fro %>%
  cbind(iso3c = fro_pts_latlon$iso3c) %>%
  mutate(data_quality = 5)

write_csv(farms_all_fro, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_fro.csv"))

@@

 - Comprehensive data

@@

farms_tas <- tas_csv %>% 
  filter(species_farmed1 == "salmon" | species_farmed2 == "salmon" | species_farmed3 == "salmon") %>%
  dplyr::select(lon, lat) %>%
  mutate(iso3c="AUS") %>%
  mutate(data_quality = 5)

write_csv(farms_tas, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_tas.csv"))

@@

farms_bc <- data.frame(do.call(rbind, st_geometry(bc_pts_latlon))) 
names(farms_bc) <- c("lon", "lat")
farms_bc <- farms_bc %>%
  mutate(iso3c="CAN") %>%
  mutate(data_quality = 5)

write_csv(farms_bc, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_bc_can.csv"))

@@

## New Brunswick

 - Comprehensive data

Source: 
NB Agriculture, Aquaculture and Fisheries, 2019. Finfish. [Accessed Oct 2019]
https://hub.arcgis.com/datasets/DAAF-MAAP::masmps-data

@@

farms_nb <- data.frame(do.call(rbind, st_geometry(nb_pts_latlon))) 
names(farms_nb) <- c("lon", "lat")
farms_nb <- farms_nb %>%
  mutate(iso3c="CAN") %>%
  mutate(data_quality = 5)

write_csv(farms_nb, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_nb_can.csv"))

@@

farms_ns <- data.frame(do.call(rbind, st_geometry(ns_pts_latlon))) 
names(farms_ns) <- c("lon", "lat")
farms_ns <- farms_ns %>%
  mutate(iso3c="CAN") %>%
  mutate(data_quality = 5)

write_csv(farms_ns, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_ns_can.csv"))

@@

farms_new_lab <- new_lab %>%
  mutate(iso3c = "CAN") %>%
  dplyr::select(lon, lat, iso3c) %>%
  mutate(data_quality = 5)

write_csv(farms_new_lab, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_new_lab_can.csv"))

@@

 - NOT comprehensive, existing points need gapfilling

@@

farms_ps <- read.csv(file.path(path, "USA/PugetSound/USA_PugetSound_AtSalmon.csv")) %>%
  mutate(iso3c = "USA") %>%
  dplyr::select(lon, lat, iso3c) %>%
  mutate(data_quality = 2)

write_csv(farms_ps, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_ps_usa.csv"))

@@

 - NOT comprehensive, existing points need gapfilling

@@

farms_us_ne <- data.frame(do.call(rbind, st_geometry(us_ne_salmon_pts_latlon))) 
names(farms_us_ne) <- c("lon", "lat")
farms_us_ne <- farms_us_ne %>%
  mutate(iso3c = "USA") %>%
  mutate(data_quality = 2)

write_csv(farms_us_ne, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_ne_usa.csv"))

@@

 - comprehensive (need to add to existing points) - We need add 22 points to existing 1 (a final total 23 of  points)

http://www.fao.org/fishery/countrysector/naso_newzealand/en
“There were 23 king salmon farms in 2004 occupying 60 hectares of water space and producing 7 400 tonnes of fish (NZAC, 2005). Most of these farms were located in marine waters in the Marlborough Sounds, and Stewart Island, but also a smaller number in freshwater in hydroelectric water channels”

@@

farms_nzl <- data.frame(do.call(rbind, st_geometry(nzl_pts_latlon))) 
names(farms_nzl) <- c("lon", "lat")
farms_all_nzl <- farms_nzl %>%
  cbind(iso3c = nzl_pts_latlon$iso3c) %>%
  mutate(data_quality = 4)

write_csv(farms_all_nzl, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_nz.csv"))

## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
nz_additional <- data.frame(iso3c = "NZL", type = "salmon", num_additional_farms = 22, data_quality = 4)
write.csv(nz_additional, here("marine/salmon/salmon_farm/data/subset_known_add_points_4/add_farms_nz.csv"), row.names = FALSE)

@@

farms_ire <- data.frame(do.call(rbind, st_geometry(ire_pts_latlon))) 
names(farms_ire) <- c("lon", "lat")
farms_ire <- farms_ire %>%
  mutate(iso3c="IRL") %>%
  mutate(data_quality = 5)

write_csv(farms_ire, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_ire.csv"))

@@

 - No info at all, needs to be fully gapfilled

@@

# farms_russia <- data.frame(lon=c(33.7149),
#                     lat=c(69.4953)) %>%
#   mutate(iso3c = "RUS") %>%
#   mutate(data_quality = 1) %>%
#   mutate(action_needed = "country based suitability")
# 
# write_csv(farms_russia, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_russia.csv"))

# Write a file for russia to indicate it has no information and will need to be fully gapfilled
rus_gf <- data.frame(iso3c = "RUS", type = "salmon", num_additional_farms = NA, data_quality = 1)
write_csv(rus_gf, here("marine/salmon/salmon_farm/data/no_info_1/gf_rus.csv"))
```

@@

farms_JPN <- data.frame(do.call(rbind, st_geometry(JPN_pts_latlon))) 
names(farms_JPN) <- c("lon", "lat")
farms_all_JPN <- farms_JPN %>%
  cbind(iso3c = JPN_pts_latlon$iso3c) %>%
  mutate(data_quality = 2)

write_csv(farms_all_JPN, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_japan.csv"))

@@

farms_dk <- cbind(farms_dk, dk_subregions ) %>%
  dplyr::select(lon, lat, iso3c, subregion = NAME) %>%
  mutate(data_quality = 5)

write.csv(farms_dk, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_denmark.csv"), row.names = FALSE)

#farms_dk <- read_csv(here("aquaculture/marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_denmark.csv"))
```

@@

http://www.fao.org/fishery/countrysector/naso_turkey/en
14 Trout and seabass farms, 6 trout farms, 1 seabass and bream and trout,  
Based on this, we will treat the FAO as truth… and spatially allocate 21 farms.

 - comprehensive - need to spatially allocate 21 farms randomly in turkey

@@

farms_turkey <- data.frame(iso3c = "TUR", type = "salmon", num_additional_farms = 21, data_quality = 3)

write_csv(farms_turkey, here("marine/salmon/salmon_farm/data/known_number_farms_3/farms_tur.csv"))

@@

# Finland
 - Comprehensive data

@@

farms_fi <- cbind(farms_fi, fi_subregions ) %>%
  dplyr::select(lon, lat, iso3c, subregion = NAME) %>%
  mutate(data_quality = 5)

write.csv(farms_fi, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_finland.csv"), row.names = FALSE)

farms_fi <- read_csv(here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_finland.csv"))
```

# Sweden

 - Comprehensive data

@@

farms_sw <- cbind(farms_sw, sw_subregions ) %>%
  dplyr::select(lon, lat, iso3c, subregion = NAME) %>%
  filter(!is.na(lat)) %>%
  mutate(data_quality = 5)

write.csv(farms_sw, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_sweden.csv"), row.names = FALSE)

#farms_sw <- read_csv(here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_sweden.csv"))
```

@@

We are using the ASC data for this, however this is only a subset of farms in Iceland. We will treat this as needed to be gapfilled with existing points (data_quality = 2)

@@

farms_ISL <- data.frame(do.call(rbind, st_geometry(ISL_pts_latlon))) 
names(farms_ISL) <- c("lon", "lat")
farms_all_ISL <- farms_ISL %>%
  cbind(iso3c = ISL_pts_latlon$iso3c) %>%
  mutate(data_quality = 2)

write_csv(farms_all_ISL, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_isl.csv"))

@@

farm_files <- list.files(here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5"), full=TRUE)
all_farms = plyr::ldply(farm_files, read_csv)

all_farms_1 <- all_farms %>%
  dplyr::select(-data_quality)

>>>>

Now we will map the remaining countries with shrimp farms that are not included in the ASC dataset. Workflow will be as follows: 
 - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
 - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
 -  If there is enough information to know there are a specific number of shrimp farms, equally allocate the farms across the coastline. If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise. 
 - Lastly, if there is no evidence of marine shrimp farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be).

For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1). 
 5: Very Good qualifications - Locations taken from leases, or from a map with specific locations
   - Must not intersect with land mask
   - "Land mask"

4: Good qualifications - Locations are projected or it is a only sample of total locations
   - Must not intersect with land mask
   - "Land mask"

3: Fair qualifications - A specific number of farms are placed on the coast, without knowing exact locations. 
   - Must be allocated spatially
   - Must not intersect with land mask
   - Flagged as "Allocate spatially"

2: Bad qualifications -  We know that aquaculture is limited to a specific subregion/state, but do not know how many or where the farms are. 
   - Must be allocated using suitability analysis.
   - Flagged as 2 and "state/province suitability"

1: Very Bad qualifications - No data at all.
   - Must be allocated using suitability analysis.
   - Flagged as 1 and "country suitability"

@@

# save as a dataframe
farms_chile <- data.frame(do.call(rbind, st_geometry(chile_pts))) 
names(farms_chile) <- c("lon", "lat")
farms_chile <- farms_chile %>%
  mutate(iso3c="CHL") %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

write_csv(farms_chile, here("marine/salmon/salmon_farm/data/farm_sites/farms_chile.csv"))

@@

We use the number of salmon licenses to get a proxy for the relative distribution of production along the Norwegian coast. 
†
## Load csv with lat long
License data.

@@

farms_nor <- sub_norway %>% 
  distinct(lon=Ø_GEOWGS84, lat=N_GEOWGS84, iso3c="NOR") %>% # Counting duplicate liscense locations once
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

write_csv(farms_nor, here("marine/salmon/salmon_farm/data/farm_sites/farms_nor.csv"))

norway <- read_csv(here("marine/salmon/salmon_farm/data/farm_sites/farms_nor.csv"))

@@

# Scotland

@@

farms_scotland$subregion <- sub_scotland$subregion
farms_scotland <- farms_scotland %>%
  mutate(iso3c = "GBR") %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

write_csv(farms_scotland, here("marine/salmon/salmon_farm/data/farm_sites/farms_scotland.csv"))

@@

@@

farms_fro <- data.frame(do.call(rbind, st_geometry(fro_pts_latlon))) 
names(farms_fro) <- c("lon", "lat")
farms_all_fro <- farms_fro %>%
  cbind(iso3c = fro_pts_latlon$iso3c) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

write_csv(farms_all_fro, here("marine/salmon/salmon_farm/data/farm_sites/farms_fro.csv"))

@@

@@

farms_tas <- tas_csv %>% 
  filter(species_farmed1 == "salmon" | species_farmed2 == "salmon" | species_farmed3 == "salmon") %>%
  dplyr::select(lon, lat) %>%
  mutate(iso3c="AUS") %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

write_csv(farms_tas, here("marine/salmon/salmon_farm/data/farm_sites/farms_tas.csv"))

@@

farms_bc <- data.frame(do.call(rbind, st_geometry(bc_pts_latlon))) 
names(farms_bc) <- c("lon", "lat")
farms_bc <- farms_bc %>%
  mutate(iso3c="CAN") %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

write_csv(farms_bc, here("marine/salmon/salmon_farm/data/farm_sites/farms_bc_can.csv"))

@@

## New Brunswick
Source: 
NB Agriculture, Aquaculture and Fisheries, 2019. Finfish. [Accessed Oct 2019]
https://hub.arcgis.com/datasets/DAAF-MAAP::masmps-data

@@

farms_nb <- data.frame(do.call(rbind, st_geometry(nb_pts_latlon))) 
names(farms_nb) <- c("lon", "lat")
farms_nb <- farms_nb %>%
  mutate(iso3c="CAN") %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

write_csv(farms_nb, here("marine/salmon/salmon_farm/data/farm_sites/farms_nb_can.csv"))

@@

farms_ns <- data.frame(do.call(rbind, st_geometry(ns_pts_latlon))) 
names(farms_ns) <- c("lon", "lat")
farms_ns <- farms_ns %>%
  mutate(iso3c="CAN") %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

write_csv(farms_ns, here("marine/salmon/salmon_farm/data/farm_sites/farms_ns_can.csv"))

@@

farms_new_lab <- new_lab %>%
  mutate(iso3c = "CAN") %>%
  dplyr::select(lon, lat, iso3c) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

write_csv(farms_new_lab, here("marine/salmon/salmon_farm/data/farm_sites/farms_new_lab_can.csv"))

@@

 - this will receive a 4 (good quality), since I do not believe it is comprehensive, and is only a sample of points.

@@

farms_ps <- read.csv(file.path(path, "USA/PugetSound/USA_PugetSound_AtSalmon.csv")) %>%
  mutate(iso3c = "USA") %>%
  dplyr::select(lon, lat, iso3c) %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

write_csv(farms_ps, here("marine/salmon/salmon_farm/data/farm_sites/farms_ps_usa.csv"))

@@

@@

farms_us_ne <- data.frame(do.call(rbind, st_geometry(us_ne_salmon_pts_latlon))) 
names(farms_us_ne) <- c("lon", "lat")
farms_us_ne <- farms_us_ne %>%
  mutate(iso3c = "USA") %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

write_csv(farms_us_ne, here("marine/salmon/salmon_farm/data/farm_sites/farms_ne_usa.csv"))

@@

@@

farms_nzl <- data.frame(do.call(rbind, st_geometry(nzl_pts_latlon))) 
names(farms_nzl) <- c("lon", "lat")
farms_all_nzl <- farms_nzl %>%
  cbind(iso3c = nzl_pts_latlon$iso3c) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

write_csv(farms_all_nzl, here("marine/salmon/salmon_farm/data/farm_sites/farms_nz.csv"))

@@

farms_ire <- data.frame(do.call(rbind, st_geometry(ire_pts_latlon))) 
names(farms_ire) <- c("lon", "lat")
farms_ire <- farms_ire %>%
  mutate(iso3c="IRL") %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

write_csv(farms_ire, here("marine/salmon/salmon_farm/data/farm_sites/farms_ire.csv"))

@@

@@

# lat long estimates from google earth
farms_russia <- data.frame(lon=c(33.7149),
                    lat=c(69.4953)) %>%
  mutate(iso3c = "RUS") %>%
  mutate(data_quality = 1) %>%
  mutate(action_needed = "country based suitability")

write_csv(farms_russia, here("marine/salmon/salmon_farm/data/farm_sites/farms_russia.csv"))

@@

farms_JPN <- data.frame(do.call(rbind, st_geometry(JPN_pts_latlon))) 
names(farms_JPN) <- c("lon", "lat")
farms_all_JPN <- farms_JPN %>%
  cbind(iso3c = JPN_pts_latlon$iso3c) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

write_csv(farms_all_JPN, here("marine/salmon/salmon_farm/data/farm_sites/farms_japan.csv"))

@@

farms_dk <- cbind(farms_dk, dk_subregions ) %>%
  dplyr::select(lon, lat, iso3c, subregion = NAME) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

write.csv(farms_dk, here("marine/salmon/salmon_farm/data/farm_sites/farms_denmark.csv"), row.names = FALSE)

#farms_dk <- read_csv(here("aquaculture/marine/salmon/salmon_farm/data/farm_sites/farms_denmark.csv"))
```

@@

Page 33 of this indicates there are 12 marine rainbow trout farms in turkey: http://tudav.org/wp-content/uploads/2018/04/marine_aquaculture_in_turkey.pdf

It says that half of those farms (6 farms) are located in Persembe bay. I will allocate the remaining 6 equally across Sinop bay, Sana bay, and Rize bay (2 farms each).

Source: 
Candan, A., Karatas, S., Kücüktas, H., Okumus, I. (Eds.), 2007. Marine aquaculture in Turkey. Türk Denzi Araştırmaları Vakfı, İstanbul.

@@

# Sinop: 2 farms, randomly picked locations
# lat 42.011686, lon 35.193134
# 42.015462, 35.168353

# Persembe: 6 farms
# 41.073031, 37.776490
# 41.071171, 37.776501
# 41.103902, 37.788303
# 41.106756, 37.788893
# 41.111485, 37.788643
# 41.114387, 37.788943

# Sana: 2 farms
# 40.991640, 39.812112
# 40.994117, 39.803345

# Rize: 2 farms
# 41.038866, 40.562498,
# 41.036462, 40.558582

farms_turkey <- data.frame(lon=c(35.193, 35.168, 37.776,  37.776, 37.788, 37.789, 37.789, 37.789, 39.812, 39.803, 40.562, 40.558),
                    lat=c(42.012, 42.015, 41.073, 41.071, 41.103, 41.106, 41.111, 41.114, 40.991, 40.994, 41.038, 41.036),
                    subregion = c("Sinop", "Sinop", "Persembe", "Persembe", "Persembe", "Persembe", "Persembe", "Persembe", "Sana", "Sana", "Rize", "Rize")) %>%
  mutate(iso3c = "TUR") %>%
  mutate(data_quality = 3) %>%
  mutate(action_needed = "Allocate spatially")

write_csv(farms_turkey, here("marine/salmon/salmon_farm/data/farm_sites/farms_tur.csv"))

@@

# Finland

@@

farms_fi <- cbind(farms_fi, fi_subregions ) %>%
  dplyr::select(lon, lat, iso3c, subregion = NAME) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

write.csv(farms_fi, here("marine/salmon/salmon_farm/data/farm_sites/farms_finland.csv"), row.names = FALSE)

farms_fi <- read_csv(here("marine/salmon/salmon_farm/data/farm_sites/farms_finland.csv"))
```

# Sweden 
Source:
HELCOM HOLAS II Dataset: Finfish mariculture, 2017. The Baltic Marine Environment Protection Commission. [Accessed October 12, 2020]

@@

farms_sw <- cbind(farms_sw, sw_subregions ) %>%
  dplyr::select(lon, lat, iso3c, subregion = NAME) %>%
  filter(!is.na(lat)) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

write.csv(farms_sw, here("marine/salmon/salmon_farm/data/farm_sites/farms_sweden.csv"), row.names = FALSE)

#farms_sw <- read_csv(here("marine/salmon/salmon_farm/data/farm_sites/farms_sweden.csv"))
```

@@

We are using the ASC data for this:

@@

farms_ISL <- data.frame(do.call(rbind, st_geometry(ISL_pts_latlon))) 
names(farms_ISL) <- c("lon", "lat")
farms_all_ISL <- farms_ISL %>%
  cbind(iso3c = ISL_pts_latlon$iso3c) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

write_csv(farms_all_ISL, here("marine/salmon/salmon_farm/data/farm_sites/farms_isl.csv"))

@@

farm_files <- list.files(here("marine/salmon/salmon_farm/data/farm_sites"), full=TRUE)
all_farms = plyr::ldply(farm_files, read_csv)

all_farms_1 <- all_farms %>%
  dplyr::select(-data_quality, -action_needed)
